FATE summary results

### 2019-11-19 paper draft.Rmd
Changed # of HMM states to 5

@@

# run each trend sequentially through the regimes
# code to identify (1) number of changes and (2)
# where those change points occur.
set.seed(99)
f1 = find_regimes(y = y[1,], sds = sd_y[1,], max_regimes = 3)

@@

@@

@@

ggsave("goa biology era sst pdo slopes.png", width=6, height=4, units="in")
```

@@

@@

>>>>

Test for regime probability. Use n=5 maximum states.

@@

# run each trend sequentially through the regimes
# code to identify (1) number of changes and (2)
# where those change points occur.
set.seed(99)
f1 = find_regimes(y = y[1,], sds = sd_y[1,], max_regimes = 5)

@@

```{r}
# try to extract annual P of each state!

kk <- plot_regime_model(f1$best_model, plot_prob_indices=c(2))

clim.regimes <- data.frame(year=1950:2019, probability=kk$data$median)

ggplot(clim.regimes, aes(year, probability)) +
  theme_bw() +
  geom_line()

# may be promising to plot all of the regime results together!

clim.regimes$data.set <- "Climate 1950-2019"
```

@@

# and combined plot

kk <- plot_regime_model(f1$best_model, plot_prob_indices=c(2))

biol.regimes <- data.frame(year=1972:2017, probability=kk$data$median)

biol.regimes$data.set <- "Biology 1972-2017"

plot.regimes <- rbind(clim.regimes, biol.regimes)

ggplot(plot.regimes, aes(year, probability, color=data.set)) +
  theme_bw() +
  geom_line()

@@

ggsave("goa biology era sst pdo slopes.png", width=6, height=4, units="in")

# make a SST-only plot
ggplot(melt.mod, aes(x=value, fill=era)) +
  theme_bw() + 
  geom_density(alpha=0.6) +
  geom_vline(xintercept = 0, lty=2) +
  scale_fill_manual(values = cb[c(4, 6, 2)]) +
  theme(legend.title = element_blank(), legend.position = c(0.8, 0.8)) +
  xlab("Slope") +
  xlim(-5,12)

ggsave("goa biology era sst slopes.png", width=5, height=4, units="in")

@@

# and combined plot

kk <- plot_regime_model(f1$best_model, plot_prob_indices=c(1))

ichthyo.regimes <- data.frame(year=plot.trend$year, probability=kk$data$median)

ichthyo.regimes$data.set <- "Ichthyoplankton 1980-2015"

plot.regimes <- rbind(clim.regimes, biol.regimes, ichthyo.regimes)

ggplot(plot.regimes, aes(year, probability, color=data.set)) +
  theme_bw() +
  geom_line()

@@

# and combined plot

kk <- plot_regime_model(f1$best_model, plot_prob_indices=c(1))

zoop.regimes <- data.frame(year=plot.trend$year, probability=kk$data$median)

zoop.regimes$data.set <- "Zooplankton 1997-2016"

plot.regimes <- rbind(clim.regimes, biol.regimes, ichthyo.regimes, zoop.regimes)

plot.regimes$plot.order <- ifelse(plot.regimes$data.set=="Climate 1950-2019", 1, 
                                  ifelse(plot.regimes$data.set=="Biology 1972-2017", 2,
                                  ifelse(plot.regimes$data.set=="Ichthyoplankton 1980-2015", 3,
                                  4)))
plot.regimes$data.set <- reorder(plot.regimes$data.set, plot.regimes$plot.order)

ggplot(plot.regimes, aes(year, probability, color=data.set)) +
  theme_bw() +
  geom_line() +
  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = 'top') + 
  scale_color_manual(values = cb[c(6,4,2,7,8)], guide=guide_legend(nrow=2))

ggsave("regime probabilities combined.png", width = 5, height = 3.5, units = "in")
